This is an example of article title

### 2025-10-30 paper/paper.tex
Maybe fix UTF8

Listing~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.}
]
function force_and_torque(sp::SystemParameters, Fθ, r)
    u, u⊥ = eachrow(Fθ)
    F, τ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.λ * E * (sp.L/(Nq-1))
        τ += sp.λ * s * dot(u⊥, E) * (sp.L/(Nq-1))
    end
    return F, τ
end

>>>>

Listing~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(sp::SystemParameters, Fθ, r)
    u, u$\bot$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u$\bot$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
